Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-11-05 chapters/chapter03.tex

\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{RacRABV_cont_vis}
\caption{
{ \footnotesize 
{\bf Screenshot of SPREAD.}
This example visualizes the phylogeographic history of rabies among raccoons along the Eastern US seaboard under a continuous diffusion model.  Such visualizations allow users to quickly inspect key evolutionary changes in their geographic context.  Further generation of KML output enables interactive exploration in the time-dimension as well in freely available virtual globe software, such as {\sc Google Earth} (on right).
}% END: footnotesize 
}
\label{fig:01}
\end{figure}

@@

For all four template analyses, SPREAD offers direct visualization but also can export the mapped objects to a keyhole markup language (KML) file suitable for viewing with virtual globe software, such as Google Earth (\url{http://earth.google.com}).
A limited example on raccoon rabies diffusion \citep{Lemey2009} finds itself in Figure~\ref{fig:01};
dynamic visualizations of this example as well as others are provided at \url{http://rega.kuleuven.be/cev/ecv/software/spread}.
KML files can be imported and visualized by many GIS software packages, including ARCGIS and Cartographica.

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{RacRABV_cont_vis}
\caption{
{ \footnotesize 
{\bf Screenshot of SPREAD.}
This example visualizes the phylogeographic history of rabies among raccoons along the Eastern US seaboard under a continuous diffusion model.  Such visualizations allow users to quickly inspect key evolutionary changes in their geographic context.  Further generation of KML output enables interactive exploration in the time-dimension as well in freely available virtual globe software, such as {\sc Google Earth} (on right).
}% END: footnotesize 
}
\label{fig:screenshot01}
\end{figure}

@@

For all four template analyses, SPREAD offers direct visualization but also can export the mapped objects to a keyhole markup language (KML) file suitable for viewing with virtual globe software, such as Google Earth (\url{http://earth.google.com}).
A limited example on raccoon rabies diffusion \citep{Lemey2009} finds itself in Figure~\ref{fig:screenshot01};
dynamic visualizations of this example as well as others are provided at \url{http://rega.kuleuven.be/cev/ecv/software/spread}.
KML files can be imported and visualized by many GIS software packages, including ARCGIS and Cartographica.
